Towards semantic-rich word embeddings

### 2019-03-21 paper/main.tex
Improve related work section

\section{Related work}
\label{related work}

Typically, there are two kinds of approach for WSD: supervised, which make use of sense-annotated training data, and knowledge-based, which make use of the properties of lexical resources. In supervised approach, the most widely used training corpus used is SemCor\cite{semcor}, with 226,036 sense annotations from 352 manually annotated documents.
Knowledge-based systems usually exploit WordNet\cite{wordnet} or BabelNet\cite{babelnet} as semantic network.
Our solution joins two approaches. We use the knowledge-based word embeddings like GloVe\cite{GloVe} as a baseline for our method and then optimize them in supervised fashion.

@@

Most of the previous neural networks applications to WSD ignore lexical resources like glosses (sense definitions) and rely solely on word's context. In Luo et al.\cite{glosses} paper, they integrate the context and glosses of the target word into a unified framework, in order to make full use of both labeled data and lexical knowledge.

Entity Linking (EL) and WSD both address the lexical ambiguity of language. The aim of EL is to discover mentions of entities within text and to link them to the most suitable entry in a reference knowledge base. The two tasks are pretty similar, but they differ fundamentally: in EL the textual mention can be linked to a named entity which may or may not contain the exact mention, while in WSD there is a perfect match between the word form and a suitable word sense in the knowledge base.
Moro et al.\cite{babelfy} present Babelfy, a unified graph-based approach to EL and WSD based on a loose identification of candidate meanings coupled with a densest subgraph heuristic, which selects high-coherence semantic interpretations.
We can find also application of random walks\cite{randomwalks} and topic models\cite{topicmodels} for knowledge-based WSD.

Developing WSD system requires much effort and as a result, very few open source WSD systems are publicly available. Zhong et al.\cite{itmakessense} present an English all-words WSD system, IMS (It Makes Sense), built using a supervised learning approach that is written in Java and completely open source. Following Lee and Ng\cite{SVMtoWSD}, they adopt support vector machines (SVM) as the classifier and integrate multiple knowledge sources including parts-of-speech (POS), surrounding words, and local collocations as features.

>>>>

\section{Related work}
\label{sec:related_work}

% Word embeddings methods:
%  Latent Semantic Analysis (LSA) and Latent Dirichlet Allocation (LDA)
%  word2vec (skip-gram and CBOW)
%  GloVe
%  fastText?
% WSD background

There have been many methods of creating semantically meaningful word representations.
Global matrix factorization methods, such as latent semantic analysis (LSA)\cite{LSA} use matrix factorization to perform rank reduction on a large term-frequency matrix, that captures statistical information about the corpus.

Local context window methods, like popular skip-gram (SG) or continuous bag-of-words (CBOW) models from word2vec paper\cite{word2vec}, were shown to outperform approaches like LSA at word analogy task.
They use shallow neural networks to either predict context words based on the current word (SG), or predict current word based on context words (CBOW).
FastText\cite{fastText} enriches skip-gram word embeddings, by representing each word as a bag of character n-grams, which also has an added benefit of the ability to compute word representations for words unseen during training.

Global Vectors (GloVe)\cite{GloVe} aim to combine both global matrix factorization and local context window methods, by training on nonzero elements in word-word co-occurence matrix, which leverages global corpus statistics and performs well on word analogy and similarity tasks.

Typically, there are two kinds of approach for Word Sense Disambiguation (WSD): supervised, which make use of sense-annotated training data, and knowledge-based, which make use of the properties of lexical resources.
%In supervised approach, the most widely used training corpus used is SemCor\cite{semcor}, with 226,036 sense annotations from 352 manually annotated documents.
Knowledge-based systems usually exploit WordNet\cite{wordnet} or BabelNet\cite{babelnet} as semantic network.
%Our solution joins two approaches. We use the knowledge-based word embeddings like GloVe\cite{GloVe} as a baseline for our method and then optimize them in supervised fashion.

@@

%Most of the previous neural networks applications to WSD ignore lexical resources like glosses (sense definitions) and rely solely on word's context. In Luo et al.\cite{glosses} paper, they integrate the context and glosses of the target word into a unified framework, in order to make full use of both labeled data and lexical knowledge.

%Entity Linking (EL) and WSD both address the lexical ambiguity of language. The aim of EL is to discover mentions of entities within text and to link them to the most suitable entry in a reference knowledge base. The two tasks are pretty similar, but they differ fundamentally: in EL the textual mention can be linked to a named entity which may or may not contain the exact mention, while in WSD there is a perfect match between the word form and a suitable word sense in the knowledge base.
%Moro et al.\cite{babelfy} present Babelfy, a unified graph-based approach to EL and WSD based on a loose identification of candidate meanings coupled with a densest subgraph heuristic, which selects high-coherence semantic interpretations.
%We can find also application of random walks\cite{randomwalks} and topic models\cite{topicmodels} for knowledge-based WSD.

%Developing WSD system requires much effort and as a result, very few open source WSD systems are publicly available. Zhong et al.\cite{itmakessense} present an English all-words WSD system, IMS (It Makes Sense), built using a supervised learning approach that is written in Java and completely open source. Following Lee and Ng\cite{SVMtoWSD}, they adopt support vector machines (SVM) as the classifier and integrate multiple knowledge sources including parts-of-speech (POS), surrounding words, and local collocations as features.
